Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-30 doc/gaia-chapter.tex
changes in gaia-chapter

This proof, as it appears inw, is quite dense and qualified as ``a bit tricky''. We present here its main steps with the help of the \alectr tool.

@@

@@

In every case, the considered ordinal is accessible. By the definition of accessibility, the ordinal \texttt{(cons a n b)} is accessible, which ends the proof. The reader is invited to replay the full proof in  \href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}, and to compare with
the proof in Section~\ref{sec:strongly-accessible}.

>>>>

This proof is quite dense and qualified as ``a bit tricky''. We just present here its main steps with the help of the \alectr tool.

The reader is invited to replay the full proof in  \href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}, and to compare with
the proof in Section~\ref{sec:strongly-accessible}.

@@

The following sentence gives us the possibility of induct over \texttt{a}'s accessibility.

\inputsnippets{nfwfgaia/nfWfProofbb}

%\inputsnippets{nfwfgaia/haveHc}

\inputsnippets{nfwfgaia/haveHd}

\inputsnippets{nfwfgaia/hdProved}

@@

In every case, the considered ordinal is accessible. By the definition of accessibility, the ordinal \texttt{(cons a n b)} is accessible, which ends the proof.
